\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-09-15 instrument.tex
Update

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage[]{arev}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Light Exposure Behavior Assessment (LEBA): Develop of a novel instrument to capture light exposure-related behaviours},
  pdfauthor={Mushfiqul Anwar Siraji1, Rafael Robert Lazar2, \& Manuel Spitschan3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

@@

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{LEBA}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours}
\author{Mushfiqul Anwar Siraji\textsuperscript{1}, Rafael Robert Lazar\textsuperscript{2}, \& Manuel Spitschan\textsuperscript{3}}
\date{}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. Mushfiqul Anwar Siraji: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Rafael Robert Lazar: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Manuel Spitschan: Data Analysis, Writing - Original Draft Preparation, Data Visualization.

Correspondence concerning this article should be addressed to Manuel Spitschan, . E-mail:

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Monash University, Malaysia\\\textsuperscript{2} University of Basel}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Describe EFA and CFA sample separately.
\item
  Sampling technique: Convince sampling (non-probability sample)
\item
  Method: cross-sectional survey
\item
  How many missing data?
\item
  How incomplete data were addressed.
\item
  Why such sample was chosen?
\end{enumerate}

EFA: For exploring initial factor structure, a sample of 250-300 is recommended (Comrey \& Lee, 1992; Schönbrodt \& Perugini, 2013)

CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule (Bentler \& Chou, 1987; Jackson, 2003; Kline, 2015; Worthington \& Whittaker, 2006) where 10 participants per parameter is required to earn trustworthiness of the result. Our sample size exceeds the requirement.

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{development-of-the-scale}{%
\subsubsection{Development of the Scale}\label{development-of-the-scale}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  How the items were generated
\item
  How the literature was reviewed to identify construct adequacy of the items.
\item
  Discuss the expert panel review process to assess content validity
\end{enumerate}

\begin{figure}

{\centering \includegraphics[width=1\linewidth,height=1\textheight]{Flowchart1}

}

\caption{Development and psychometric properties of LEBA }\label{fig:unnamed-chunk-1}
\end{figure}

\hypertarget{procedure-1}{%
\subsection{Procedure}\label{procedure-1}}

Our study had four objectives. First, to develop an instrument to assess an individual's light exposure behavior. Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure. The third one is to gather structural validity evidence for the latent structure obtained in EFA. Lastly, we gathered item information using Item response theory (IRT)(Baker, 2017)

\hypertarget{data-collection}{%
\subsubsection{Data Collection}\label{data-collection}}

Timeline of data collection,
ethical approval
mode of data collection
how consent was recorded.

\hypertarget{analytic-strategies}{%
\subsection{Analytic Strategies}\label{analytic-strategies}}

We used R (version 4.1.0), including several R packages, for our analyses. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix (C. Desjardins \& Bulut, 2018) for the EFA. We employed principal axis (pa) a factor extraction method with varimax rotation. PA is robust to the normality assumption violations (Watkins, 2020). The obtained latent structure was confirmed by the minimum residuals extraction method as well. We used a combination factor identification method including scree plot(Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method(Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers. Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors {[}Bandalos and Finney (2018);

\hypertarget{results}{%
\section{Results}\label{results}}

Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy(Kaiser, 1974) . The overall KMO vale for 48 items was 0.63 which was above the cutoff value (.50) indicating a mediocre sample (Hutcheson, 1999).

\begin{center}
\begin{ThreePartTable}

\begin{TableNotes}[para]
\normalsize{\textit{Note.} *p<.001}
\end{TableNotes}

\begin{longtable}{ccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:tabDes}Descriptive Statistics}\\
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:tabDes} continued}}\\
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
\endhead
Item1 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81* & .25\\
Item2 & 2.87 & 1.59 & 0.08 & -1.60 & 0.81* & .19\\
Item3 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87* & .16\\
Item4 & 1.47 & 1.18 & 2.38 & 4.00 & 0.43* & .28\\
Item5 & 4.01 & 1.40 & -1.22 & 0.07 & 0.70* & .13\\
Item6 & 2.79 & 1.55 & 0.19 & -1.48 & 0.85* & .20\\
Item7 & 2.26 & 1.25 & 0.70 & -0.60 & 0.85* & .19\\
Item8 & 2.97 & 1.20 & -0.06 & -0.94 & 0.91* & -.10\\
Item9 & 2.94 & 1.03 & -0.12 & -0.40 & 0.91* & .10\\
Item10 & 2.74 & 1.04 & 0.09 & -0.74 & 0.91* & .28\\
Item11 & 2.18 & 0.90 & 0.60 & 0.12 & 0.86* & .26\\
Item12 & 2.36 & 1.22 & 0.59 & -0.62 & 0.87* & .25\\
Item13 & 2.73 & 1.46 & 0.20 & -1.36 & 0.87* & .33\\
Item14 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80* & .26\\
Item15 & 3.26 & 1.09 & -0.26 & -0.45 & 0.80* & .14\\
Item16 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50* & .32\\
Item17 & 1.54 & 1.21 & 2.07 & 2.75 & 0.49* & .31\\
Item18 & 1.12 & 0.49 & 5.02 & 27.80 & 0.25* & .16\\
Item19 & 1.05 & 0.36 & 7.23 & 52.98 & 0.13* & .18\\
Item20 & 1.04 & 0.33 & 8.99 & 85.28 & 0.10* & .16\\
Item21 & 1.14 & 0.59 & 4.79 & 24.05 & 0.25* & .16\\
Item22 & 3.57 & 1.07 & -0.65 & -0.17 & 0.88* & .21\\
Item23 & 2.56 & 1.27 & 0.33 & -1.00 & 0.89* & .11\\
Item24 & 4.14 & 0.99 & -1.23 & 1.14 & 0.79* & .19\\
Item25 & 2.59 & 1.41 & 0.27 & -1.27 & 0.86* & .19\\
Item26 & 2.25 & 1.27 & 0.69 & -0.64 & 0.84* & .18\\
Item27 & 3.80 & 1.29 & -0.87 & -0.42 & 0.82* & .17\\
Item28 & 3.76 & 1.14 & -0.68 & -0.45 & 0.86* & .00\\
Item29 & 2.44 & 1.31 & 0.38 & -1.14 & 0.86* & .11\\
Item30 & 1.48 & 1.11 & 2.18 & 3.35 & 0.48* & .24\\
Item31 & 3.00 & 1.62 & -0.08 & -1.61 & 0.83* & .44\\
Item32 & 3.55 & 1.65 & -0.60 & -1.34 & 0.76* & .43\\
Item33 & 3.62 & 1.64 & -0.68 & -1.25 & 0.74* & .32\\
Item34 & 3.42 & 1.83 & -0.45 & -1.69 & 0.69* & .33\\
Item35 & 3.86 & 1.67 & -0.99 & -0.85 & 0.65* & .23\\
Item36 & 1.54 & 1.25 & 2.13 & 2.86 & 0.46* & .36\\
Item37 & 1.33 & 0.91 & 3.03 & 8.43 & 0.41* & .01\\
Item38 & 4.30 & 1.08 & -1.79 & 2.53 & 0.67* & .22\\
Item39 & 1.96 & 0.98 & 1.02 & 0.69 & 0.82* & .05\\
Item40 & 2.16 & 1.19 & 0.71 & -0.54 & 0.84* & .14\\
Item41 & 1.31 & 0.81 & 2.75 & 6.92 & 0.43* & .21\\
Item42 & 3.93 & 1.48 & -1.06 & -0.44 & 0.71* & .18\\
Item43 & 1.64 & 1.18 & 1.79 & 2.02 & 0.60* & .15\\
Item44 & 3.51 & 1.30 & -0.70 & -0.59 & 0.85* & .39\\
Item45 & 2.22 & 1.48 & 0.71 & -1.02 & 0.76* & .30\\
Item46 & 1.76 & 1.23 & 1.35 & 0.44 & 0.66* & .38\\
Item47 & 2.11 & 1.17 & 0.77 & -0.39 & 0.83* & .32\\
Item48 & 2.60 & 1.25 & 0.29 & -0.86 & 0.89* & .35\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

\end{ThreePartTable}
\end{center}

\begin{figure}

{\centering \includegraphics[width=0.5\linewidth]{manuscript_files/figure-latex/figCor-1}

}

\caption{Correlation plot of the items}\label{fig:figCor}
\end{figure}

Table\ref{tab:tabDes} summarizes the univariate descriptive statistics for the 48 items. some of the items were skewed with high Kurtosis values. Our data violated both univariate normality (Shapiro-Wilk statistics; (Shapiro \& Wilk, 1965)) and multivariate normality assumptions (Marida's test;(Mardia, 1970)). Multivariate skew was = 583.80 (p \textless0.001) and multivariate kurtosis was = 2,749.15 (p \textless0.001). Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen (C. Desjardins \& Bulut, 2018). Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA. However only 4.96\% of the inter-item correlation coefficients were greater than .30. The inter item correlation ranged between .44 to .91. And the corrected item-total correlations ranged between .10 to .44.

Scree plot ( Figure \ref{fig:facid}) suggested a six-factor solution. Horn's parallel analysis (Horn, 1965) with 500 iterations also indicated a six-factor solution. However, the MAP method (Velicer, 1976) and Hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) suggested a five-factor solution. As a result, we tested both five-factor and six-factor solutions.

\begin{figure}

{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{parallel} \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/facid-2} \includegraphics[width=0.5\linewidth,height=0.5\textheight]{HUll method}

}

\caption{Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method}\label{fig:facid}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1.2\linewidth,height=1\textheight]{EFAplot.LR}

}

\caption{Five Factor Solution}\label{fig:EFAplot}
\end{figure}

Three rounds of EFA starting with all 48 items were conducted and problematic items were gradually discarded (cross-loading items and poor factor loading (\textless.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30. We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary). Table\ref{tab:TabEFA5} displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from -.49 to .99 indicating strong coefficients. The commonalities ranged between .11 to .99. However, the histogram of the absolute values of non-redundant residual-correlations (Fig\ref{fig:Residuals} showed 26.00\% correlations greater than the absolute value of .05, indicating a possible under-factoring. (C. D. Desjardins, 2018). Subsequently, we fitted a six-factor solution. However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.

In the five-factor solution, the first factor contained three items and explained 10.25\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) = .86). All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments. The second factor contained six items and explained 9.93\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) = .71). Items under this factor commonly investigate an individual's hours spent outdoor. The third factor contained five items and explained 8.83\% of the total variance. Items under this factor dealt with the specific behaviors pertaining to sleep. However, the internal consistency reliability coefficient was not satisfactory (\(\alpha\) = .68). The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, \(\alpha\) = .62. These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time. Lastly, the fifth factor contained six items and explained 6.14\% of the total variance.This factor tried to measure an individual's behavior lead by the awareness of light's influence on health. However, this factor showed unsatisfactory internal consistency reliability (\(\alpha\) = .53). It is essential to attain a balance between psychometric properties and the interpretability of the common themes when exploring the latent structure. As all of the emerged factors are highly interpretable, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA). Two items showed negative factor-loading (items 44 and 21). Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:TabEFA5}}

\begin{tabular}{ccccccc}
\toprule
 & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{F2} & \multicolumn{1}{c}{F3} & \multicolumn{1}{c}{F4} & \multicolumn{1}{c}{F5} & \multicolumn{1}{c}{Communality}\\
\midrule
item16 & 0.99 & - & - & - & - & 0.99\\
item36 & 0.94 & - & - & - & - & 0.9\\
item17 & 0.8 & - & - & - & - & 0.66\\
item11 & - & 0.8 & - & - & - & 0.64\\
item10 & - & 0.76 & - & - & - & 0.59\\
item12 & - & 0.65 & - & - & - & 0.47\\
item7 & - & 0.5 & - & - & - & 0.27\\
item8 & - & -0.5 & - & - & - & 0.25\\
item9 & - & 0.32 & - & - & - & 0.11\\
item27 & - & - & 0.8 & - & - & 0.66\\
item3 & - & - & 0.8 & - & - & 0.68\\
item40 & - & - & 0.65 & - & - & 0.46\\
item30 & - & - & 0.45 & - & - & 0.35\\
item41 & - & - & -0.36 & - & - & 0.33\\
item33 & - & - & - & 0.74 & - & 0.56\\
item32 & - & - & - & 0.73 & - & 0.62\\
item35 & - & - & - & 0.66 & - & 0.45\\
item37 & - & - & - & -0.39 & - & 0.17\\
item38 & - & - & - & 0.36 & - & 0.18\\
item46 & - & - & - & - & 0.6 & 0.42\\
item45 & - & - & - & - & 0.59 & 0.37\\
item25 & - & - & - & - & 0.41 & 0.19\\
item4 & - & - & - & - & 0.41 & 0.22\\
item1 & - & - & - & - & 0.4 & 0.17\\
item26 & - & - & - & - & 0.39 & 0.17\\
internal Consistency & .86 & .71 & .68 & .62 & .53 & -\\
\% of variance & 10.25 & 9.93 & 8.83 & 8.44 & 6.14 & -\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Only loading higher than .30 is reported}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\begin{figure}

{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/Residuals-1}

}

\caption{ Histogram of residulas:  five-factor solution}\label{fig:Residuals}
\end{figure}

\hypertarget{confirmatory-factor-analysis}{%
\section{Confirmatory Factor Analysis}\label{confirmatory-factor-analysis}}

\hypertarget{irt}{%
\subsection{IRT}\label{irt}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Helvetica}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Light Exposure Behavior Assessment (LEBA): Long and Short Form},
  pdfauthor={Mushfiqul Anwar Siraji, Rafael Robert Lazar, Juliëtte van Duijnhoven, Luc Schlangen, Shamsul Haque, Vineetha Kalavally, Céline Vetter, Gena Glickman, Karin Smolders, \& Manuel Spitschan},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{LEBA}
\usepackage{csquotes}
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form}
\author{Mushfiqul Anwar Siraji\textsuperscript{}, Rafael Robert Lazar\textsuperscript{}, Juliëtte van Duijnhoven\textsuperscript{}, Luc Schlangen\textsuperscript{}, Shamsul Haque\textsuperscript{}, Vineetha Kalavally\textsuperscript{}, Céline Vetter\textsuperscript{}, Gena Glickman\textsuperscript{}, Karin Smolders\textsuperscript{}, \& Manuel Spitschan\textsuperscript{}}
\date{}

\affiliation{\phantom{0}}

@@

\textbf{Disclaimer}: This is a non-public version of LEBA and still a work in progress.

LEBA captures light exposure-related behaviours on a 5 point Likert type scale ranging from 1 to 5 (Never =1; Rarely= 2; Sometimes =3; Often = 4; Always =5). The score of each factor is calculated by the summation of scores of items belonging to the corresponding factor.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
Long Form (23 Items) \\
\midrule
\endhead
\textbf{F1: Blue Filter} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1 hour before attempting to fall asleep. \\
\textbf{F2: Natural Light} \\
I spend 30 minutes or less per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
I spend more than 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
\textbf{F3: Smart Device} \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I look at my mobile phone screen immediately after waking up. \\
I check my phone when I wake up at night. \\
I look at my smartwatch within 1 hour before attempting to fall asleep. \\
I look at my smartwatch when I wake up at night. \\
\textbf{F4: Sleep Environment} \\
I dim my mobile phone screen within 1 hour before attempting to fall asleep. \\
I use a blue-filter app on my computer screen within 1 hour before attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
I dim my computer screen within 1 hour before attempting to fall asleep. \\
\textbf{F5: Electric Light} \\
I use tunable lights to create a healthy light environment. \\
I use LEDs to create a healthy light environment. \\
I use a desk lamp when I do focused work. \\
I use an alarm with a dawn simulation light. \\
I turn on the lights immediately after waking up. \\
\bottomrule
\end{longtable}
